---
title: "Stats Final Project"
author: "Aparna Devi Akula"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Doing analysis on YouTube data seems very interesting to me, so I decide to consider YouTube data.
This dataset is a daily record of the top trending YouTube videos.
This dataset includes several months of data on daily trending YouTube videos. Data is included 
for the USA, Great Britain, Germany, Canada, and France with up to 200 listed trending videos per day.
But for my analysis I considered only USA dataset. This data is in a separate file. 
Data includes the video title, channel title, publish time, tags, views, likes and dislikes, 
description, and comment count. So with the data I am doing visualizations that tells us how views,
likes,dislikes,comment_count,trending date and some other variables are related to each other.
I also developed two models to find out which model is efficient for this particular dataset and 
what is the accuracy of the predicted models.** 

### Declaring the required packages
```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dplyr)
library(tinytex)
```
### Importing data
```{r}
youtube = read_csv("C:/Users/Akula/Downloads/USvideos.csv")
glimpse(youtube)
```
The dataset obtained is clear and there is no need to clean the data, so considering the original dataset itself.



### Rearranging data as per convenience
```{r}
youtube <- youtube %>% mutate(views_per_million = views/1000000)
youtube <- youtube %>% mutate(likes_per_million = likes/1000000)
youtube <- youtube %>% mutate(dislikes_per_million = dislikes/1000000)
```
Converting view,likes and dislikes to views_per_million,likes_per_million and dislikes_per_million 
respectively as per convenience.



### How many channels have the videos greater 50 million views?
```{r}
youtube %>% filter(views_per_million>50) %>%
  ggplot(aes(x=channel_title,y=views_per_million)) + geom_point(aes(x=channel_title,y=views_per_million)) +     geom_line(aes(group=1))+ theme(legend.position = "bottom", axis.text.x = element_text(angle = 90))
```

20 channels have the videos which have more than 50 million views. Two channels each have two videos 
that have more than 50 million views.



### Which video has the highest and lowest likes?
```{r}
youtube %>% filter(likes==0 | likes==5613827 )
```
"BTS (ë°©íƒ„ì†Œë…„ë‹¨) 'FAKE LOVE' Official MV" has the highest likes with 5.61 million and 
there are 30 videos have zero likes.



### Which video has the highest and lowest dislikes?
```{r}
youtube %>% filter(dislikes==0 | dislikes==1674420 )
```
"So Sorry" video has highest number of dislikes with 1.6 million, and there are 100 videos which have zero dislikes

### The videos which have zero likes and zero dislikes.
```{r}
youtube %>% filter(likes==0 & dislikes==0) %>% select(title)
```
There are 29 videos which have no likes and no dislikes.


### To the videos which have more than 50 million views,how are their corresponding views and likes?
```{r fig.height=7}
youtube_above50 <- youtube %>% filter(views_per_million>50)
youtube_above50 %>% ggplot() + 
      geom_point(aes(x=title,y=views_per_million,color = "views_per_million")) + 
      geom_point(aes(x=title,y=likes_per_million,color = "likes_per_million")) +
      theme(legend.position = "bottom", axis.text.x = element_text(angle = 90))
```

The video "Childish Gambino - This Is America (Official Video)" has 225 million views but it has 5 million likes only,
where as "BTS (방탄소년단) 'FAKE LOVE' Official MV" video has 5.6 million likes which is highest likes but the views 
are 123 million.


```{r}
youtube_above50 <- youtube %>% filter(views_per_million>50)
```
Filtering and creating a list with the views greater for 50 million



### How many videos have disabled commenting?
```{r}
youtube_comments <- as_tibble(c("Comments Enabled","Comments Disabled"))
youtube_comments <- youtube_comments %>% add_column(n = c(6329,111))
ggplot(youtube_comments, aes(x="", y = n,fill=value)) +
  geom_bar(stat="identity", width=1) +coord_fixed() +
  coord_polar("y",start = 0)
```

Nearly 111 videos have disabled the comments out of 6440 videos



### How many videos have disabled ratings?
```{r}
youtube_ratings <- as_tibble(c("Ratings Enabled","Ratings Disabled"))
youtube_ratings <- youtube_ratings %>% add_column(n = c(6410,28))
ggplot(youtube_ratings, aes(x="", y = n,fill=value)) +
  geom_bar(stat="identity", width=1) +coord_fixed() +
  coord_polar("y",start = 0)
```

About 28 videos ratings have been disabled and for 6410 videos ratings are enabled



### Comparing likes and dislikes for the videos which have more than 50 million views.
```{r fig.height=6}
p1 <- youtube_above50 %>% ggplot(aes(x=title,y=likes_per_million)) +    
  geom_point(aes(x=title,y=likes_per_million))+
  geom_line(aes(group=1),color = "red")+  
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90)) 

p2 <- youtube_above50 %>% ggplot(aes(x=title,y=dislikes_per_million))+
  geom_point(aes(x=title,y=dislikes_per_million)) +
  geom_line(aes(group=1),color = "blue") +  
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90))

plot(p1)
plot(p2)
```

"BTS (방탄소년단) 'FAKE LOVE' Official MV" video has highest likes which is 5.6 million and 0.2 million dislikes.
"YouTube Rewind:The Shape of 2017|#YouTubeRewind" has highest dislikes as 1.6 million.
We can say that with the increase of likes there is simultaneous increase in dislikes



### Which video got most trended? (videos that has greater than 50 million views)
```{r}
youtube_above50 %>%  ggplot(aes(x=trending_date,y=title))+
  geom_point(aes(x=trending_date,y=title)) +
  geom_line(aes(group=1)) + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90))
```

"YouTube Rewind:The Shape of 2017|#YouTubeRewind" is the video that got most trended, in the 
videos that has greater than 50 million views.
Based on the above two visualizations we can say that the video which is most trending is the 
video which got the highest number of dislike.(videos that has greater than 50 million views.)



Converting publish date and trending date to time format
```{r}
youtube <- youtube %>% add_column(trendingdate = as.Date(youtube$trending_date,format="%y.%d.%m"))
youtube <- youtube %>% add_column(publish_date = as.Date(youtube$publish_time,format="%y-%d-%m"))
```

Finding trend difference
```{r}
youtube_above50 <- youtube %>% filter(views_per_million>50)
youtube_above50 <- youtube_above50 %>% mutate(trending_diff = trendingdate - publish_date)
```

### How many days after the publish date did the videos start trending?(for videos that has greater than 50 million views)
```{r}
youtube_above50 %>% ggplot(aes(x=trending_diff,y=title))+
  geom_bar(stat="identity", width=0.5) + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90))
```

"YouTube Rewind: The Shape of 2017 | #YouTubeRewind by YouTube Spotlight", "Bruno Mars - Finesse (Remix) 
[Feat. Cardi B] [Official Video] by Bruno Mars" and "42 HOLY GRAIL HACKS THAT WILL SAVE YOU A FORTUNE 
by 5-Minute Crafts" -- these 3 videos took less time to get trending, after 8 days from the publish date 
these videos started to trend. 



### How trending date and publish date effect likes_per_million? (for videos that has greater than 50 million views)
```{r fig.height=7}
ggplot(youtube_above50) + geom_bar(aes(y=trending_diff,x=title),stat="identity", width=0.5) + 
  geom_point(aes(y=likes_per_million, x=title),stat="identity",color="red") + 
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(sec.axis=sec_axis(~.*0.01,name="Likes_per_million"))
```

Trending_diff doesn't really effect anything on the likes, its just the increase in the number of views per video.



### Linear Model
```{r}
model <- lm(views~likes+dislikes+comment_count, data=youtube)
summary(model)
coefficients(model)
ggplot(data = youtube,aes(x=views,y=comment_count))+geom_point()+geom_smooth(method = 'lm')
```

It can be clearly seen from the linear model that views are co-related with likes,dislike and comment count.
and with the increase in the number of views there will an increase in the comment count



### Providing some more insights based on the linear model.
```{r BTS fans only commenting}
youtube_above50 <- youtube_above50 %>% mutate(commentcount_views = comment_count/views)
```


### Comparing Commentcount with respective to views
```{r fig.height=6}
youtube_above50 %>% ggplot(aes(x=title,y=commentcount_views))+geom_point()+geom_smooth() +  
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90))
```

I did a calculation commentcount_views which is comment_count/views, if the ratio is equal to 1,
we can determine that the number of views to the video is equal to the number of comments that video have.
From the plot we can see that BTS is in the ratio of 0.01, this means "BTS'FAKE LOVE' Official MV" 
is the only video among the videos that have more than 50 million views, that has its 
number of views nearer to the comment count.



### Dividing the data into test data and train data
```{r}
train_data <- youtube[0:5000,]
test_data <- youtube[5001:6440,]
```


### Anova Model
```{r}
model3 <- lm(views~dislikes,data=train_data)
anova(model3)
plot(model3)
```

This technique is used to answer the hypothesis while analyzing multiple groups of data. 
This is done using views and dislikes. 



### Developing a Linear Model based on the train data based on views,tredingdate,likes and dislike.
```{r}
model2 <- lm(views~trendingdate+likes+dislikes,data=train_data)
summary(model2)
coefficients(model2)
ggplot(data = train_data,aes(x=views,y=likes))+geom_point()+geom_smooth(method = 'lm')
```

It can be clearly seen from the linear model that views are co-related with trending date,likes and dislikes.
and with the increase in the number of views there will an increase in the number of likes.



### Calculating predicted views based on the test data using the linear model that is developed for train data.
```{r}
predicted <- data.frame(predict = predict(model2, newdata = test_data))
glimpse(predicted)
```
### Calculating error value based on the predicted data we derived.
```{r}
error <- data.frame(e_value = (predicted$predict - test_data$views)/predicted$predict * 100)
mean(error$e_value)
```

We can see the error as 35% so there is only 65% accuracy in the predicated data, which is low.



### Developing Generalized Linear Model using the train data
```{r}
glm_model <- glm(views~trendingdate+likes+dislikes,data=train_data)
summary(glm_model)
```

It can be determined from the Generalized Linear Model that views are co-related with trending date,
likes and dislikes.



### How much accuracy  be derived using the Generalized Linear Model
```{r}
library(performance)
performance_accuracy(glm_model)
```

We can see that the accuracy is 83.62% meaning there is only 16.38% of error.



### Comparing the two models developed on views ~ trendingdate + likes + dislikes
```{r}
models <- c('Linear Model','Generalized Linear Model')
accuracy_values <- c(65,81.51)
ggplot()+ geom_bar(aes(x = models, y = accuracy_values, fill = accuracy_values),stat = 'identity')
```

From the bar chart above, it can be concluded that Generalized Linear Model is more efficient than 
Linear Model for the opted data.



### References:-
https://www.kaggle.com/datasnaek/youtube-new/data?select=USvideos.csv
https://stat412612.netlify.app/
https://stackoverflow.com/questions/28320228/put-one-line-chart-and-bar-chart-in-one-plot-in-r-not-ggplot
https://www.educba.com/anova-in-r/
http://web.stanford.edu/class/stats306a/RforGLM.pdf
https://www.educba.com/bar-charts-in-r/
https://r4ds.had.co.nz/model-basics.html


